Agile Inter-team Software Development

### 2019-01-21 Draft/Parts/Conclusion.tex
Minor fixes to random stuff.

\section{Conclusion} 
\label{sec:conclusion}
As we have seen, inter-team communication can be an obstacle in agile teams working on the same thing as intermediaries in communication and lack of common personal causes things to go haywire if left unchecked.
To reduce this problem a number of small additions can be done to the process as specified but the most important part of the change is a good architecture and design which is available to all the teams and thus provides a common framework to all the teams involved.

>>>>

\section{Conclusion}\label{sec:conclusion}
As we have seen, inter-team communication can be an obstacle in agile teams working on the same thing as intermediaries in communication and lack of common personal causes things to go haywire if left unchecked.
To reduce this problem a number of small additions can be done to the process as specified but the most important part of the change is a good architecture and design which is available to all the teams and thus provides a common framework to all the teams involved.

### 2019-01-21 Draft/Parts/Main.tex
Minor fixes to random stuff.

\section{Spotify: A Canonical Example} 
\label{sec:spt_ex} 
For a typical example of a company using many agile teams, consider Spotify who has over 30 teams \cite{kniberg12}.
The basic element of the development organization at Spotify is the Squad, analogous to a Scrum team.
Each Squad is the autonomous developer, with a localized working area, of a particular sub-system in the product.
Squads in related areas are grouped together into Tribes. 
The overall structure is illustrated in Figure~\ref{fig:spotify_structure}.
Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.

@@

\subsection{Communication}
%social fixes
A fundamental issue with tasking teams with different goals is that teams can become isolated with respect to the context of their work.
At Spotify \cite{kniberg12}, offices are laid out so that the Squads making up a Tribe are spatially close. This leads to an environment where an informal exchange of information on the Tribes work will occur.
%second problem
Consider another scenario: a tester on a particular agile team invests time to solve a particular problem, which is also faced by another tester on a different team. Without communication, these team members would perform redundant work.
To address this problem Spotify defines Chapters \cite{kniberg12}, which are crosscutting divisions which gathers individuals with similar roles across different Squads.

\section{Proposed Approach}
\label{sec:prop_appro} 
The general problem of communication can be tackled from two perspectives.
First, stakeholders at different levels need to have ways to pass information.
This can be addressed by adaptions in development process and leveraging technology.
Second, the quality of communication needs to be accurate.
This can be addressed by sound system specification through architecture and design.

@@

\subsection{Technology Improvements} 
\label{sec:tech_impv}
	A good technology stack can be a powerful tool in maintaining a widely distributed team.
	Good communication and management tools can help the teams in keeping track of things that they need to do so that other teams can work as intended.
	The following are some of the areas where the technology can assist the teams in making a more efficient agile process environment.

%Communication Tools
As agile focuses on personal interaction with highest importance given to face-to-face conversation, conferencing tools such as video conferencing and WebEx etc. can help the team interactions become more fluid and clearer.
They also make the communication real-time thus removing the lag in process due to time spent in communicating ideas across teams.

%Integration Tools
Continuous integration tools can go a long way in finding out inter-team problems early in the process as every time any team makes a change, its impact on the entire project can be seen.

@@

In addition to specification of system elements, architecture can also be used to empower teams.
As discussed by Parnas \cite{Parnas72}, there are two general approaches to decomposing systems: 1) compartmentalizing a computational process and, 2) focusing on information hiding.
The latter approach ideal for agile development since this approaches defines system components in terms of design dicisions, which empowers invidual teams.

>>>>

\section{Spotify: A Canonical Example} 
\label{sec:spt_ex} 
For an example of a company using many agile teams, consider Spotify who has over 30 teams \cite{kniberg12}.
The basic element of development organization at Spotify is the Squad, analogous to a Scrum team.
Each Squad is the autonomous developer, with a localized working area, of a particular sub-system in the product.
Squads in related areas are grouped together into Tribes. 
The overall structure is illustrated in Figure~\ref{fig:spotify_structure}.
Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.

@@

\subsection{Communication at Spotify}
%social fixes
A fundamental issue with tasking teams with different goals is that teams can become isolated with respect to the context of their work.
At Spotify \cite{kniberg12}, offices are laid out so that the Squads making up a Tribe are spatially close. This leads to an environment where an informal exchange of information on the Tribes work will occur.
%second problem
Consider another scenario: a tester on a particular agile team invests time to solve a particular problem, which is also faced by another tester on a different team. Without communication, these team members would perform redundant work.
To address this problem Spotify defines Chapters \cite{kniberg12}, which are crosscutting divisions which gathers individuals with similar roles across different Squads.

\section{Communication in Inter-team Development}
\label{sec:prop_appro} 
The general problem of communication can be tackled from two perspectives.
First, stakeholders at different levels need to have ways to pass information.
This can be addressed by adaptions in development process and leveraging technology.
Second, the quality of communication needs to be accurate.
This can be addressed by sound system specification through architecture and design.
%In Section ~\ref{sec:proc_impv}, we discuss the adaptations to an agile process, and team structure, to support better collaboration between teams.
%In Section ~\ref{sec:tech_impv}, we discuss the ways in which technology improve inter-team communication
%In Section ~\ref{sec:imp_of_dsgn}, we discuss the role of architecture and design in mitigating communication issues.

@@

\subsection{Technology Approaches} \label{sec:tech_impv}
Selecting an appropriate technology stack plays an important role maintaining a widely distributed team.
Technology can help teams in keeping track of things that they need to do so that other teams can work efficiently.
The following are some of the areas where the technology can enable a more efficient agile process environment.

%Communication Tools
Since agile focuses on personal interaction, particularly face-to-face conversation, video conferencing tools can help the team interactions become more fluid and clearer.
They also make the communication real-time thus removing the delay in process due to time spent in communicating ideas across teams.
%Integration Tools
Continuous integration tools can go a long way in finding out inter-team problems early in the process as every time any team makes a change, its impact on the entire project can be seen.

@@

In addition to specification of system elements, architecture can also be used to empower teams.
As discussed by Parnas \cite{Parnas72}, there are two general approaches to decomposing systems: 1) compartmentalizing a computational process and, 2) focusing on information hiding.
The latter approach ideal for agile development since this approaches defines system components in terms of design decisions, which empowers individual teams.
